### 2017-03-22 paper/oopsla17-submission/evaluation.tex
ugh, start typign up the eval

\pgfplotstableset{col sep=comma}

\pgfplotstableread{../../data/sp14/op+type+size/linear/results.csv}{\FeatureLinearBench}
\pgfplotstablevertcat{\FeatureLinearBench}{../../data/sp14/op+context+type+size/linear/results.csv}
\pgfplotstablevertcat{\FeatureLinearBench}{../../data/sp14/op+context-has+type+size/linear/results.csv}
\pgfplotstablevertcat{\FeatureLinearBench}{../../data/sp14/op+context-count+type+size/linear/results.csv}
\pgfplotstableread{../../data/sp14/op+type+size/hidden-10/results.csv}{\FeatureHiddenTBench}
\pgfplotstablevertcat{\FeatureHiddenTBench}{../../data/sp14/op+context+type+size/hidden-10/results.csv}
\pgfplotstablevertcat{\FeatureHiddenTBench}{../../data/sp14/op+context-has+type+size/hidden-10/results.csv}
\pgfplotstablevertcat{\FeatureHiddenTBench}{../../data/sp14/op+context-count+type+size/hidden-10/results.csv}
\pgfplotstableread{../../data/sp14/op+type+size/hidden-500/results.csv}{\FeatureHiddenFHBench}
\pgfplotstablevertcat{\FeatureHiddenFHBench}{../../data/sp14/op+context+type+size/hidden-500/results.csv}
\pgfplotstablevertcat{\FeatureHiddenFHBench}{../../data/sp14/op+context-has+type+size/hidden-500/results.csv}
\pgfplotstablevertcat{\FeatureHiddenFHBench}{../../data/sp14/op+context-count+type+size/hidden-500/results.csv}

\pgfplotstableread{../../data/sp14/op+type+size/hidden-10/results.csv}{\HiddenBench}
\pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+type+size/hidden-25/results.csv}
\pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+type+size/hidden-50/results.csv}
\pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+type+size/hidden-100/results.csv}
\pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+type+size/hidden-250/results.csv}
\pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+type+size/hidden-500/results.csv}
% \pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+context-count+type+size/hidden-10/results.csv}
% \pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+context-count+type+size/hidden-25/results.csv}
% \pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+context-count+type+size/hidden-50/results.csv}
% \pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+context-count+type+size/hidden-100/results.csv}
% \pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+context-count+type+size/hidden-250/results.csv}
% \pgfplotstablevertcat{\HiddenBench}{../../data/sp14/op+context-count+type+size/hidden-500/results.csv}

\pgfplotstableread{../../data/sp14/baseline.csv}{\SpringBench}
\pgfplotstablevertcat{\SpringBench}{../../data/sp14/ocaml/results.csv}
\pgfplotstablevertcat{\SpringBench}{../../data/sp14/mycroft/results.csv}
\pgfplotstablevertcat{\SpringBench}{../../data/sp14/sherrloc/results.csv}
\pgfplotstablevertcat{\SpringBench}{../../data/sp14/op+type+size/linear/results.csv}
\pgfplotstablevertcat{\SpringBench}{../../data/sp14/op+type+size/decision-tree/results.csv}
\pgfplotstablevertcat{\SpringBench}{../../data/sp14/op+type+size/hidden-10/results.csv}
\pgfplotstablevertcat{\SpringBench}{../../data/sp14/op+type+size/hidden-250/results.csv}

\pgfplotstableread{../../data/fa15/baseline.csv}{\FallBench}
\pgfplotstablevertcat{\FallBench}{../../data/fa15/ocaml/results.csv}
\pgfplotstablevertcat{\FallBench}{../../data/fa15/mycroft/results.csv}
\pgfplotstablevertcat{\FallBench}{../../data/fa15/sherrloc/results.csv}
\pgfplotstablevertcat{\FallBench}{../../data/fa15/op+type+size/linear/results.csv}
\pgfplotstablevertcat{\FallBench}{../../data/fa15/op+type+size/decision-tree/results.csv}
\pgfplotstablevertcat{\FallBench}{../../data/fa15/op+type+size/hidden-10/results.csv}
\pgfplotstablevertcat{\FallBench}{../../data/fa15/op+type+size/hidden-250/results.csv}

@@

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{axis}[
  % ybar stacked,
  width=12cm,
  height=8cm,
  title={Impact of Feature Set on Accuracy},
  ylabel={Accuracy},
  %ymin=0.2,
  ymax=1,
  yticklabel={\pgfmathparse{\tick*100}\pgfmathprintnumber{\pgfmathresult}\,\%},
  ytick style={draw=none},
  ymajorgrids = true,
  symbolic x coords={op+type+size, op+context+type+size, op+context-has+type+size, op+context-count+type+size},
  % enlarge x limits=0.25,
  xtick=data,
  xtick style={draw=none},
  xticklabels={Type, Context-Is, Context-Has, Context-Count},
  x tick label style={rotate=45},
  reverse legend,
  transpose legend,
  legend style={legend pos = outer north east, legend columns=4},
]
% \addplot[draw=black, fill=blue1] table[x=tool, y=top-1] {\HiddenBench};
% \addplot[draw=black, fill=blue2] table[x=tool, y expr=\thisrow{top-2} - \thisrow{top-1}] {\HiddenBench};
% \addplot[draw=black, fill=blue3] table[x=tool, y expr=\thisrow{top-3} - \thisrow{top-2}] {\HiddenBench};

\addplot[mark options={fill=blue1, scale=1.5}, mark=square*]
  table[x=features, y=top-1] {\FeatureHiddenFHBench};
\addplot[mark options={fill=blue2, scale=1.5}, mark=square*]
  table[x=features, y=top-2] {\FeatureHiddenFHBench};
\addplot[mark options={fill=blue3, scale=1.5}, mark=square*]
  table[x=features, y=top-3] {\FeatureHiddenFHBench};
\addlegendentry{Top 1}
\addlegendentry{Top 2}
\addlegendentry{Top 3}
\addlegendimage{empty legend}
\addlegendentry{\hiddenFH}

\addplot[mark options={fill=blue1, scale=1.5}, mark=*]
  table[x=features, y=top-1] {\FeatureLinearBench};
\addplot[mark options={fill=blue2, scale=1.5}, mark=*]
  table[x=features, y=top-2] {\FeatureLinearBench};
\addplot[mark options={fill=blue3, scale=1.5}, mark=*]
  table[x=features, y=top-3] {\FeatureLinearBench};
\addlegendentry{Top 1}
\addlegendentry{Top 2}
\addlegendentry{Top 3}
\addlegendimage{empty legend}
\addlegendentry{\linear}

\end{axis}
\end{tikzpicture}
\caption{reuslts!}
\label{fig:results}
\end{figure}

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{axis}[
  ybar stacked,
  width=12cm,
  height=8cm,
  title={Impact of Hidden Layer Size on Accuracy},
  ylabel={Accuracy},
  bar width=20pt,
  %ymin=0.2,
  ymax=1,
  yticklabel={\pgfmathparse{\tick*100}\pgfmathprintnumber{\pgfmathresult}\,\%},
  ytick style={draw=none},
  ymajorgrids = true,
  symbolic x coords={op+type+size/hidden-10, op+type+size/hidden-25, op+type+size/hidden-50,
                     op+type+size/hidden-100, op+type+size/hidden-250, op+type+size/hidden-500},
  % enlarge x limits=0.25,
  xtick=data,
  xtick style={draw=none},
  xticklabels={\hiddenT, \hiddenTF, \hiddenF, \hiddenH, \hiddenTHF, \hiddenFH},
  x tick label style={rotate=45},
  reverse legend,
  legend style={legend pos = north west},
]
\addplot[draw=black, fill=blue1] table[x=tool, y=top-1] {\HiddenBench};
\addplot[draw=black, fill=blue2] table[x=tool, y expr=\thisrow{top-2} - \thisrow{top-1}] {\HiddenBench};
\addplot[draw=black, fill=blue3] table[x=tool, y expr=\thisrow{top-3} - \thisrow{top-2}] {\HiddenBench};
% \addplot[draw=black, fill=blue1] table[x=tool, y=top-1] {\HiddenBench};
% \addplot[draw=black, fill=blue2] table[x=tool, y=top-2] {\HiddenBench};
% \addplot[draw=black, fill=blue3] table[x=tool, y=top-3] {\HiddenBench};
\legend{Top 1, Top 2, Top 3}
\end{axis}
\end{tikzpicture}
\caption{reuslts!}
\label{fig:results}
\end{figure}

>>>>

\input{data}

\subsection{Experimental Setup}
\label{sec:experimental-setup}

\subsection{Type Error Slice}
\label{sec:type-error-slice}
The \InSlice feature should be highly predictive --- a fix must change
at least one expression in the type-error slice.
%
Thus, our first experiment seeks to quantify the impact of \InSlice by
comparing the accuracy of a linear model on three sets of features.
%
\begin{enumerate}
\item A baseline with only local syntactic features.
\item extends (1) with \InSlice.
\item discards samples from (1) where \InSlice is \emph{disabled}.
\end{enumerate}
%
The key difference between (2) and (3) is that a model for (2) must
\emph{learn} that \InSlice is a strong predictor.
%
In contrast, a model for (3) must only learn about the syntactic
features, the decision to discard samples where \InSlice is disabled has
already been made by a human.
%
This has a few additional advantages: it reduces the search space by a
factor of 7 on average, and it guarantees that any prediction made by
the classifier can fix the type error.
%
We expect that (2) will perform better than (1) as it has more
information, and that (3) will perform better than (2) as it does not
have to learn the importance of \InSlice.

We tested our hypothesis with a linear model cross-validated ($k=10$)
over the combined SP14/FA15 dataset. We used a learning rate
$\alpha=0.001$, L2 regularization rate $\lambda=0.001$, and mini-batch
size of 200. We trained for a single epoch on feature sets (1) and
(2), and for 8 epochs on (3), so that the total number of training samples
would be roughly equal for each feature set.

\begin{table}[ht]
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Feature Set  & Top-1  & Top-2  & Top-3  & Recall \\
    \midrule
    Local Syntax & 23.6\% & 42.6\% & 56.3\% & 19.6\% \\
    With Slice   & 46.4\% & 65.0\% & 75.4\% & 30.4\% \\
    Only Slice   & 54.9\% & 71.4\% & 82.5\% & 57.6\% \\
    \bottomrule
  \end{tabular}
  \caption{
    Impact of type-error slice on accuracy.
    \ES{TODO: expand caption}
    \ES{TODO: load these numbers from CSV}
  }\label{tab:type-error-slice}
\end{table}

\autoref{tab:type-error-slice} shows the results of our experiment.
%
As expected the baseline performs the worst, with a mere 23.6\% Top-1
accuracy.
%
Adding \InSlice improves the results substantially with a 46.4\% Top-1
accuracy, demonstrating the importance of a minimal error slice.
%
However, filtering out expressions that are not part of the slice
\emph{further} improves the results to 54.9\% Top-1 accuracy.
%
Clearly, some decisions are too important to be left to a machine.

Note also the jump in Recall when we filter out expressions that are not
part of the error slice.
%
Reducing the search space not only improves our chances of making a
single correct prediction, it also allows us to make \emph{multiple}
correct predictions per program.

Given the decisive benefits of filtering out expressions that do not
belong to the type-error slice, we will assume going forward that
\emph{all} data sets have been filtered.

\subsection{Contextual Features}
\label{sec:contextual-features}

Next, we will investigate the relative impact of the other three classes
of features discussed in \autoref{sec:features}.
%
For this we consider again a baseline of only local syntactic features,
extended by each combination of
%
(1) expression size,
(2) contextual syntactic features, and
(3) typing features.
%
As before we perform a 10-fold cross-validation with a learning rate and
L2 regularization rate of 0.001 and a mini-batch size of 200, but we
train for a full 10 epochs.

\begin{table}[ht]
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Feature Set                 & Top-1  & Top-2  & Top-3  & Recall \\
    \midrule
    Local Syntax                & 55.0\% & 71.6\% & 82.6\% & 57.7\% \\
    \midrule
    + Size                      & 55.8\% & 72.8\% & 82.5\% & 57.3\% \\
    + Contextual Syntax         & 59.9\% & 77.7\% & 86.4\% & 63.0\% \\
    + Types                     & 62.2\% & 77.7\% & 85.7\% & 62.2\% \\
    \midrule
    + Size + Contextual Syntax  & 60.2\% & 77.9\% & 86.0\% & 62.5\% \\
    + Size + Types              & 62.0\% & 78.2\% & 85.6\% & 62.3\% \\
    + Contextual Syntax + Types & 63.2\% & 80.3\% & 87.9\% & 65.4\% \\
    \midrule
    + All                       & 62.3\% & 80.0\% & 88.0\% & 65.4\% \\
    \bottomrule
  \end{tabular}
  \caption{
    Impact of contextual features on accuracy.
    \ES{TODO: expand caption}
    \ES{TODO: load these numbers from CSV}
  }\label{tab:type-error-slice}
\end{table}

@@

% \begin{figure}[ht]
% \centering
% \begin{tikzpicture}
% \begin{axis}[
%   % ybar stacked,
%   width=12cm,
%   height=8cm,
%   title={Impact of Feature Set on Accuracy},
%   ylabel={Accuracy},
%   %ymin=0.2,
%   ymax=1,
%   yticklabel={\pgfmathparse{\tick*100}\pgfmathprintnumber{\pgfmathresult}\,\%},
%   ytick style={draw=none},
%   ymajorgrids = true,
%   symbolic x coords={op+type+size, op+context+type+size, op+context-has+type+size, op+context-count+type+size},
%   % enlarge x limits=0.25,
%   xtick=data,
%   xtick style={draw=none},
%   xticklabels={Type, Context-Is, Context-Has, Context-Count},
%   x tick label style={rotate=45},
%   reverse legend,
%   transpose legend,
%   legend style={legend pos = outer north east, legend columns=4},
% ]
% % \addplot[draw=black, fill=blue1] table[x=tool, y=top-1] {\HiddenBench};
% % \addplot[draw=black, fill=blue2] table[x=tool, y expr=\thisrow{top-2} - \thisrow{top-1}] {\HiddenBench};
% % \addplot[draw=black, fill=blue3] table[x=tool, y expr=\thisrow{top-3} - \thisrow{top-2}] {\HiddenBench};

% \addplot[mark options={fill=blue1, scale=1.5}, mark=square*]
%   table[x=features, y=top-1] {\FeatureHiddenFHBench};
% \addplot[mark options={fill=blue2, scale=1.5}, mark=square*]
%   table[x=features, y=top-2] {\FeatureHiddenFHBench};
% \addplot[mark options={fill=blue3, scale=1.5}, mark=square*]
%   table[x=features, y=top-3] {\FeatureHiddenFHBench};
% \addlegendentry{Top 1}
% \addlegendentry{Top 2}
% \addlegendentry{Top 3}
% \addlegendimage{empty legend}
% \addlegendentry{\hiddenFH}

% \addplot[mark options={fill=blue1, scale=1.5}, mark=*]
%   table[x=features, y=top-1] {\FeatureLinearBench};
% \addplot[mark options={fill=blue2, scale=1.5}, mark=*]
%   table[x=features, y=top-2] {\FeatureLinearBench};
% \addplot[mark options={fill=blue3, scale=1.5}, mark=*]
%   table[x=features, y=top-3] {\FeatureLinearBench};
% \addlegendentry{Top 1}
% \addlegendentry{Top 2}
% \addlegendentry{Top 3}
% \addlegendimage{empty legend}
% \addlegendentry{\linear}

% \end{axis}
% \end{tikzpicture}
% \caption{reuslts!}
% \label{fig:results}
% \end{figure}

% \begin{figure}[ht]
% \centering
% \begin{tikzpicture}
% \begin{axis}[
%   ybar stacked,
%   width=12cm,
%   height=8cm,
%   title={Impact of Hidden Layer Size on Accuracy},
%   ylabel={Accuracy},
%   bar width=20pt,
%   %ymin=0.2,
%   ymax=1,
%   yticklabel={\pgfmathparse{\tick*100}\pgfmathprintnumber{\pgfmathresult}\,\%},
%   ytick style={draw=none},
%   ymajorgrids = true,
%   symbolic x coords={op+type+size/hidden-10, op+type+size/hidden-25, op+type+size/hidden-50,
%                      op+type+size/hidden-100, op+type+size/hidden-250, op+type+size/hidden-500},
%   % enlarge x limits=0.25,
%   xtick=data,
%   xtick style={draw=none},
%   xticklabels={\hiddenT, \hiddenTF, \hiddenF, \hiddenH, \hiddenTHF, \hiddenFH},
%   x tick label style={rotate=45},
%   reverse legend,
%   legend style={legend pos = north west},
% ]
% \addplot[draw=black, fill=blue1] table[x=tool, y=top-1] {\HiddenBench};
% \addplot[draw=black, fill=blue2] table[x=tool, y expr=\thisrow{top-2} - \thisrow{top-1}] {\HiddenBench};
% \addplot[draw=black, fill=blue3] table[x=tool, y expr=\thisrow{top-3} - \thisrow{top-2}] {\HiddenBench};
% % \addplot[draw=black, fill=blue1] table[x=tool, y=top-1] {\HiddenBench};
% % \addplot[draw=black, fill=blue2] table[x=tool, y=top-2] {\HiddenBench};
% % \addplot[draw=black, fill=blue3] table[x=tool, y=top-3] {\HiddenBench};
% \legend{Top 1, Top 2, Top 3}
% \end{axis}
% \end{tikzpicture}
% \caption{reuslts!}
% \label{fig:results}
% \end{figure}
